\begin{rubric}{Miscellaneous Experience}
\subrubric{Organization}
\entry*[2025 -- $\cdots$] Software Engineering at Montreal -- Meeting at UdeM
\entry*[2024 -- $\cdots$] International workshop on collaborative and participatory modeling (MODELS co-located workshop) 
\subrubric{Reviews for Journals}
\entry*[2025 -- $\cdots$] Empirical Software Engineering
\entry*[2025 -- $\cdots$] ACM Transactions on Software Engineering and Methodology
\entry*[2025 -- $\cdots$] Information and Software Technology
\entry*[2024 -- $\cdots$] Software and Systems Modeling
\entry*[2024 -- $\cdots$] Automated Software Engineering
\entry*[2023 -- $\cdots$] Journal of Systems and Software
\entry*[2022 -- $\cdots$] Journal of Software: Evolution and Process

\subrubric{Reviews for Conferences and Workshops}
\entry*[2025 -- $\cdots$] International Conference on Software Analysis, Evolution and Reengineering (SANER) -- Research track
\entry*[2025 -- $\cdots$]  International Systems and Software Product Line Conference (SPLC) -- Main Track
\entry*[2025 -- $\cdots$]  International Conference on Evaluation and Assessment in Software Engineering (EASE) -- Short papers and Emerging Results Track
\entry*[2025 -- $\cdots$]  International Conference on Model Driven Engineering Languages and Systems (MODELS) -- Tools and Demonstrations Track
\entry*[2025 -- $\cdots$] International Conference on Software Testing, Verification and Validation (ICST) -- Posters Track
\entry*[2024 -- $\cdots$] First International Workshop on Model Management (MODELS co-located workshop) 
\entry*[2023 -- $\cdots$] Re:Volution (SPLC co-located workshop)
\subrubric{Awards and Achievements}
\entry*[2025] \textbf{JKU Young Researchers' Award} for the thesis ``Improving Consistency Maintenance for Collaborative Software Systems Engineering'' 
\entry*[2024] \textbf{Distinguished Paper Award}, SANER 2024. For the paper ``Exploring dependencies among inconsistencies to enhance the consistency maintenance of models''%
\entry*[2022] \textbf{SoSym-First Paper Award}, MODELS 2022. For the paper ``Generating repairs for inconsistent models''%
\entry*[2022] \textbf{Best Paper Award}, ICSSP/ICGSE 2022. For the paper ``Change-oriented repair propagation''%
\entry*[2021]
\textbf{Best Master Thesis}, Software Engineering Doctoral and Master Theses Competition - Brazil.
\entry*[2019]
\textbf{Student with the most outstanding performance in the Software Engineering Masters Course}, Universidade Federal do Pampa.
\entry*[2018]
\textbf{Student with the most outstanding performance in the Software Engineering Undergraduate Course}, Universidade Federal do Pampa.
\entry*[2016]
\textbf{Student with the most outstanding performance in the Software Engineering Undergraduate Course}, Universidade Federal do Pampa.
\entry*[2014] \textbf{Dean's List Certificate}, Illinois Institute of Technology School of Applied Technology.

% \subrubric{Certification}
% \entry*[2014] \textbf{Certified XYZ Practioner}. Awarded by X Insitute.
% \entry*[2006] \textbf{Certified Level 3 in ABC}. Awarded by ABC.

\end{rubric}